---
title: "dplyr summarise bug?"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, message=F}
library(tidyverse)
stats <- read_csv('stats.csv')
```
I am pretty sure that I got the same behaviour before I updated `Rcpp`.

```{r}
sessionInfo()
```

### Use `filter` and `invoke_map` to performance group aggregation

```{r}
test <- function(impl, size) {
  stats %>%
    filter(message.size==size & implementation==impl) %>%
    select(ts.in, ts.out) %>%
    summarise(begin=min(ts.in),
              end=max(ts.out),
              process.time=end - begin,
              message.rate=size * 10000/as.double(process.time)/1024/1024)
}

invoke_map_df(test, crossing(impl=c('Camel', 'Spark'), size=c(1024, 1024*5, 1024*10)) %>% transpose())
```

### Using `group_by` and `summarise`

```{r}
stats %>%
  group_by(implementation, message.size) %>%
  summarise(total.size=sum(message.size), 
            begin=min(ts.in), 
            end=max(ts.out), 
            duration=end-begin,
            message.rate=total.size/as.numeric(duration)/1024/1024) %>%
  ungroup() %>%
  select(begin, end, duration, message.rate)
```

For some reason the `process.time` is not calculated correctly, but supprisingly `message.rate` which depends on it is correct! Did I do something wrong here?

### Using `group_by` and `do`

```{r}
stats %>%
  group_by(implementation, message.size) %>%
  do(tibble(total.size=sum(.$message.size), 
            begin=min(.$ts.in), 
            end=max(.$ts.out), 
            duration=end-begin,
            message.rate=total.size/as.numeric(duration)/1024/1024)) %>%
  ungroup() %>%
  select(begin, end, duration, message.rate)
```

Do's behaviour matches `filter` and `invoke_map` combination.